\large\bfseries Soliton Solution, B\"acklund Transformation, Conservation Laws, and rogue wave solution for a generalized variable-coefficient Sasa-Satsuma-like equation

### 2018-03-12 me/paper/paper.tex
update

\title{\large\bfseries Soliton Solution, Ba\"cklund Transformation, Conservation Laws, and rogue wave solution for a generalized variable-coefficient Sasa-Satsuma-like equation}
\author{}

@@

\section{Introduction}
Sasa-Satsuma equation (SSE) is one of the nonlinear evolution equations (NLEEs), which has attracted much attentions and studied in recent years. It is used to describe and explain many phenomenons in different fields such as fluid dynamics, plasma physics, and optical fiber communications.

>>>>

\title{\large\bfseries Soliton Solution, B\"acklund Transformation, Conservation Laws, and rogue wave solution for a generalized variable-coefficient Sasa-Satsuma-like equation}
\author{}

@@

\section{Introduction}
Sasa-Satsuma equation (SSE) is one of the nonlinear evolution equations (NLEEs), which has attracted much attentions and studied in recent years. It is used to describe and explain many phenomenons in different fields such as fluid dynamics, plasma physics, and optical fiber communications. When under different conditions or complex scenes, the variable-coefficient NLEEs are able to describe various situations more realistically than their constant-coefﬁcient counterparts. In this Letter we will investigate a generalized and expanded Sasa-Satsuma equation with variable coefficients as follows,
\begin{align}
  & \mathrm{i}u_{t} + a_{1}(t)u_{xx} + a_2(t)|u|^{2}u + a_3(t)\mathrm{i}u_{xxx} + a_{4}(t)\mathrm{i}(|u|^{2}u)_{x} + a_{5}(t)\mathrm{i}(|u|^{2})_{x}u + a_{6}(t)u \notag\\
  & + a_{7}(t)\mathrm{i}u_{x}=0,
\end{align}
where $u$ denotes the complex envelope of the wave field, and all coefficients $a_{1}(t), \cdots, a_{6}(t)$ are real functions of $t$, describing the effects of group velocity dispersion, self-phase modulation, third order dispersion, self-steepening and self-frequency shifting via stimulated Raman scattering respectively.

This Letter is arranged as follows. In Section 2, based on the extended AKNS system, the Lax pair of Eq.(1) will be constructed. In Section 3, Riccati-type auto-B\"acklund transformations will be presented and then one-soliton of Eq.(1) will be provided via the obtained B\"acklund transformation. And an infinite number of recursive conservation laws will be derived in Section 4. In Section 5, A twisted rogue-wave pair will be given under certain constraints. Finally, we will get conclusion and discussion in Section 6.

\section{Lax Pair}
    The Lax pair
